On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-17 MS.tex
Suggested edits on abstract

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits. Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.

\item Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations). As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e. juvenile, sapling and adult).

\item Results were consistent with predictions. Specific leaf area was correlated with GR in juvenile but not in adult plants. Correlations of GR with wood density and assimilation rate were not affected by stage. Maximum height and seed mass were correlated with GR only in one plant stage category.

\item Synthesis: We show that traits-GR correlations change in a predictable way as a function of plant size. Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.

>>>>

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits. Yet, the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.

\item We propose that traits should influence growth in a way that depends on the plant's size. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations). To cpature the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: juvenile, sapling and adult.

\item Results were consistent with predictions. Specific leaf area was correlated with GR in juvenile but not in adult plants. Correlations of GR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with GR only in one plant stage category: juveniles and adults, respectively.

\item Synthesis: We show how trait-GR correlations change in a predictable way with plant size. These  Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
